---
output:
  github_document:
    html_preview: false
always_allow_html: true
---

# vegTemplates

A collection of automatic documents using the package
[`yamlme`](https://github.com/kamapu/yamlme/).

## Installation

To install the development version, use the package
[`remotes`](https://remotes.r-lib.org/):

```{r eval=FALSE}
library(remotes)
install_github("kamapu/vegTemplates")
```

## Get ready in advance

Before you use this package, you need to know the structure of objects defined
as classes [`taxlist`](https://docs.ropensci.org/taxlist/) and
[`vegtable`](https://github.com/kamapu/vegtable/).
For the first case you can take a look into the article written by [Alvarez &
Luebert (2018)](https://doi.org/10.3897/bdj.6.e23635).

Next to it, you may need experience working with
[`rmarkdown`](https://rmarkdown.rstudio.com/) and perhaps
[LaTeX](https://latex.org/) and [`knitr`](https://yihui.org/knitr/), as well.
They will be here implemented by the package
[`yamlme`](https://kamapu.github.io/rpkg/yamlme/).

## Examples

### Taxonomic checklist

Here an automatic checklist using the example data set released in the package
`taxlist` (called **Easplist**).

```{r eval = FALSE}
library(taxlist)
library(vegTemplates)

check_list(Easplist, output_file = "ea-checklist", exclude = "family",
    prefix = c(family = "# "), output = "html_document")
```

```{r echo = FALSE, message = FALSE, results = "hide"}
library(taxlist)
library(vegTemplates)

check_list(Easplist, output_file = "pkgdown/assets/ea-checklist", exclude = "family",
    prefix = c(family = "# "), output = "html_document")
```

With the option `'exclude = "family"'` you prevent family names to be
formatted in italics.
With the option `'prefix = c(family = "# ")'` you add a markdown command
to set families as sections in the document.
With the option `'output = "html_document"'` we set the output as a HTML
document instead of the default PDF.

Check the output
[here](ea-checklist.html).
